EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-05-15 draft.tex
comment
Eliminates some comments, small changes

  \begin{tabular}{lll}
  \hline
  Dim & Env         & Median of ratio \\
  \hline
  10  & Local       & \textbf{47,166.29}       \\
      & Multi task  & 40,466.45    \\
      & Single task & 18,193.05      \\
  \hline
  20  & Local       & \textbf{36,101.86}   \\
      & Multi task  & {\ul 33,916.02}       \\ % why the underline?
      & Single task & 16,546.95  \\
  \hline
  \end{tabular}
\end{table}

@@

  \includegraphics[width=0.30\textwidth]{GAOnly_f005}&
  \includegraphics[width=0.30\textwidth]{PSOOnly_f005}&
  \includegraphics[width=0.30\textwidth]{GAPSO_f005}\\
  \end{tabular}
  \vspace{-3ex}
   \caption{
Scaling of expected runtime (RT defined as the number of function 
evaluations \#FE) to reach a target for  
each dimension. Target values $\Delta f$ = 10, 1, $10^{-1}$, $10^{-2}$,$10^{-3}$,$10^{-5}$,$10^{-8}$
(the exponent and colors are given in the legend of $f_1$). 
Lines are the average RT; Cross ($+$): median RT of successful runs to reach
the most difficult target that was reached at least once;
Cross (\textcolor{red}{$\times$}): maximum \#FE in any trial. 
Values are divided by dimension and plotted as $log_{10}$.
The light thick line with diamonds indicates the theoretical best algorithm from BBOB 2009 for the 
most difficult target.
% More explanation for those not familiar with BBOB - JJ
% I think is more clear? - M
% Almost everything, but the cream-colored rhombs in the bottom...
}
\label{fig:bbob}
\end{figure*}

@@

A multi-population based algorithm can decrease the execution time
because of parallel execution. But, having heterogeneous 
populations might enhance evolutionary search and avoid unneeded
evaluations more than homogeneous systems systems do; heterogeneous settings, if
done right, increases the diversity of the whole population\cite{araujo2008multikulti}.

@@

The results obtained by the experiments show (see Figure \ref{fig:bbob}) how
the runtime scales with dimension to reach certain target values $\Delta f$;
The color of the lines indicates the average runtime, for each target reached
at least once. A red circle without a number on top indicates the algorithm
has reached the $10^{-8}$ target on all instances for that dimension. If there
is that number, it indicates how many times the algorithm has reached
the target. Fixed values of targets $\Delta f = 10^{k}$ with $k$ colors are
given in the legend of $f_1$ in the top row, $k$ values are $[-8,-5,-3,-2,-1,0,1]$. Results
from each configuration are presented in each column, GA, PSO, and GA\&PSO
populations. % clarify which colors for every level - JJ
% colors are shown in the figure, I put a hint that is in the top row. 
% But I can list them if that is better - M

>>>>

  \begin{tabular}{lll}
  \hline
  Dim & Env         & Median of ratio \\
  \hline
  10  & Local       & \textbf{47,166.29}       \\
      & Multi task  & 40,466.45    \\
      & Single task & 18,193.05      \\
  \hline
  20  & Local       & \textbf{36,101.86}   \\
      & Multi task  & {\ul 33,916.02}       \\ % why the underline? [Best between cloud options :) - Mario] Then why not above too? - JJ
      & Single task & 16,546.95  \\
  \hline
  \end{tabular}
\end{table}

@@

  \includegraphics[width=0.30\textwidth]{GAOnly_f005}&
  \includegraphics[width=0.30\textwidth]{PSOOnly_f005}&
  \includegraphics[width=0.30\textwidth]{GAPSO_f005}\\
  \end{tabular}
  \vspace{-3ex}
   \caption{Scaling of expected runtime (RT defined as the number of function 
evaluations \#FE) to reach a target for  
each dimension. Target values $\Delta f$ = 10, 1, $10^{-1}$, $10^{-2}$,$10^{-3}$,$10^{-5}$,$10^{-8}$
(the exponent and colors are given in the legend of $f_1$). 
Lines are the average RT; Cross ($+$): median RT of successful runs to reach
the most difficult target that was reached at least once;
Cross (\textcolor{red}{$\times$}): maximum \#FE in any trial. 
Values are divided by dimension and plotted as $log_{10}$.
The light thick line with diamonds indicates the theoretical best algorithm from BBOB 2009 for the 
most difficult target.
}
\label{fig:bbob}
\end{figure*}

@@

A multi-population based algorithm can decrease the execution time
thanks to running the algorithm on several populations at the same
time. But, if the populations are heterogeneous 
it might enhance evolutionary search and avoid unneeded
evaluations to a greater extent than homogeneous systems systems do; heterogeneous settings, if
done right, increase the diversity of the whole population\cite{araujo2008multikulti}.

@@

The results obtained by the experiments show (see Figure \ref{fig:bbob}) how
the runtime scales with dimension to reach certain target values $\Delta f$;
The color of the lines indicates the average runtime, for each target reached
at least once. A red circle without a number on top indicates the algorithm
has reached the $10^{-8}$ target on all instances for that dimension. If there
is that number, it indicates how many times the algorithm has reached
the target. Fixed values of targets $\Delta f = 10^{k}$ with $k$ colors are
given in the legend of $f_1$ in the top row, $k$ values are $[-8,-5,-3,-2,-1,0,1]$. Results
from each configuration are presented in each column, GA, PSO, and GA\&PSO
populations.
